Writing News Captions with Bags of Attention

### 2019-10-22 paper/paper.tex
Add works on transformer captioning

@@

This motivates us to recollect data from the New York Times in a more careful
manner. We call this NYTimes+.

>>>>

Zhu \etal \cite{Zhu2018CaptioningTW} used transformers to achieve competitive
results on the MSCOCO dataset. Li \etal \cite{Li2019Boosted} added attention
over image regions and semantic concepts using Faster-RCNN
\cite{Ren2015FasterRCNN}. Both of these works, however, used the MSCOCO dataset
which contains generic captions with no named entities.

@@

This motivates us to recollect data from the New York Times in a more careful
manner, using our own parser. We call this NYTimes+.
